Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-14 code/rmarkdown/article.Rmd
+ article fixes + extra refs

Here we investigate the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation in the context of conservation planning. Conventionally, prioritizations are generated by setting targets on the total amount of habitat that needs to be preserved for each species (amount-based targets), and finding the combination of planning units that fulfills all the targets for minimal cost [eg. using \texttt{Marxan}; @r22]. First, we aim to verify that environmental and geographic variables are effective surrogates for adaptive and neutral variation (respectively). We expect that prioritizations generated using surrogate-based targets will secure more genetic variation than prioritizations generated using only amount-based targets with the same number of planning units. Second, we aim to determine if the addition of surrogate-based targets to conservation planning exercises can result in more effective prioritizations. We expect that prioritizations generated using amount- and surrogate-based targets will sufficiently preserve the genetic variation of more species than those generated using only amount-based targets. If these surrogates can improve the intra-specific genetic variation captured in a prioritization, then conservation planners may use these surrogates when genetic data is not available, and in turn deliver more effective protected areas.

## Methods
### Study system
We used species distribution and genomic data collected by the IntraBioDiv project in the European Alps [@r451; see @r452 and @r478 for further explanation of data collection methods]. This data set was particularly well suited for our study because it contains genetic data for a diverse range of species that were collected using the same sampling regime. Additionally, the study area covers a broad geographic domain that encompasses attitudinal gradients. As part of this project, data were collected for 27 alpine plant species using a 20' longitude by 21' latitude grid (approx. 22.3 km $\times$ 25 km; Figure S1). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using amplified fragment length polymorphisms [AFLP; @r453], and constructed matrices denoting the presence/absence of polymorphisms at loci for each species. Thus the data set contains information describing the genomic variation of individuals for each species present in every second grid cell. We used these grid cells as planning units to develop prioritizations. To reduce computational effort, we used only grid cells that contained at least a single individual ($n = `r nrow(grid.DF)`$). The majority of our analyses were performed using the \texttt{R} software package [version `r paste0(version$major, '.', version$minor)`; @r192].

### Landscape data
We examined the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation (respectively). To describe the geographic location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each grid cell, we obtained 19 bioclimatic variables [approx. 1 km resolution; @r33]. These layers and the grid cells were projected into an equal-area coordinate system ($\texttt{ESRI:102014}$). The bioclimatic variables were clipped to the extent of the grid and subject to a principal components analysis (PCA; using \texttt{ArcMap} version 10.2.2; Table S1). The first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components (PCs) cumulatively explained `r round(pca.DF[[4]][surrogate.params.LST[[MODE]]$number.components],1)` % of the variation and were used to generate two new layers. We calculated the average value for each PC layer in each grid cell, and used these values to characterize the main themes of climatic variation among the grid cells (Figure S2). The cost of purchasing land for preservation often exerts a strong influence on which planning units are recommended for prioritization [reviewed in @r482]. To examine the potential effects of cost, we calculated the total human population density inside each planning unit [obtained at 1 km resolution from the Global Rural-Urban Mapping Project; \texttt{GRUMP V1}; @r472] and used this to represent acquisition cost.

### Adaptive and neutral genetic data
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were under selection. We used outlier detection methods [compared in @r454; reviewed in @r480] to achieve this. The basic premise underpinning these analyses is that neutral loci are expected to exhibit a specific level of variation among populations ($F_{st}$), and loci that deviate from this expectation should be under selection. The advantage of these methods--in contrast with environmental association analyses [eg. @r475]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. In an earlier study, Bothwell _et al._ [-@r455] applied such outlier detection methods to one of the species in this data set (_Gentiana nivalis_). Here, we adopted a similar methodology and applied it to each of the 27 species in the data set.

First, we grouped individuals into genetic lineages for each species [using a methodology similar to that implemented in \texttt{prabclust R} package; @r479]. The purpose of this step was to avoid falsely classifying loci as adaptive. For each species, we ordinated the genomic data, and then fit models to the ordinated data to group individuals into populations. Specifically, we used non-metric multi-dimensional scaling [NMDS; implemented in the $\texttt{vegan R}$ package; @r458] using Gower distances [@r464; using the $\texttt{cluster R}$ package to accommodate sparsity; @r457] to transform the binary loci data into continuous variables (Table S2). To ensure that the ordinations described a sufficient amount of the genomic variation, we ran successive scaling analyses with increasing dimensionality until this was achieved (maximum stress value $\leq$ `r nmds.params.LST[[MODE]]$population.clustering$max.stress`; `r nmds.params.LST[[MODE]]$population.clustering$trymax` random starts for each analysis). We then fit a suite of Gaussian mixture models to the ordinations to estimate the probability that individuals belonged to different populations [assuming different covariance structures implemented in the \texttt{mclust R} package; @r477; @r476]. For each parametrization, we fit a set of models assuming varying numbers of total populations (\textit{G}= 1--`r max(mclust.params.LST[[MODE]]$G)`). We identified the most parsimonious model for each species (lowest Bayesian Information Criterion $BIC$ statistic; Figures S4), and used them to group individuals to populations (Figure S5).

After grouping individuals into populations, we identified the loci under selection (Table S3). Since outlier detection methods compare allele frequencies between populations, we were unable to examine species that contained a single population. These species were omitted from subsequent analysis ($n = `r sum(sapply(spp.Mclust.LST, function(x) return(ncol(x$mclust$z)==1)))`$). For the remaining species, we ran $\texttt{Bayescan}$ [version 2.1; 1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. To avoid false-positives, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the user manual) and assumed they were neutral. Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r mclust.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate to ensure convergence [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species (Figures S6--S32). For each species, we partitioned adaptive and neutral loci into separate data sets, and reran the successive nonmetric multidimensional scaling analyses (using parameters described above but with maximum stress values $\leq$ `r nmds.params.LST[[MODE]]$genetic.space$max.stress`) to derive continuous variables that described the main gradients of adaptive and neutral genetic variation separately (Table S2). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the individuals in each grid cell to express the typical genomic characteristics of individuals in the cells.

### Prioritizations
We used the unreliable representative and adequate prioritization (URAP) formulation of the reserve selection problem [@r465]. This formulation can identify the minimum number of planning units required to preserve both a proportion of the species' range (using amount-based targets) and a proportion of the species' intra-specific variation [using space-based targets and attribute spaces; _sensu_ @r465]. We treated the environmental and geographic surrogate variables as separate attribute spaces. We also treated the adaptive (if detected) and neutral variables as separate attribute spaces for each species. We set the demand points for each species and each attribute space using the values associated with the planning units. For every prioritization we generated, we calculated the proportion of the adaptive (if detected) and neutral genetic variation that every prioritization secured to assess its performance. Prioritizations associated with negative values--because they secured only a very small amount of genetic variation--were replaced with zeros to facilitate statistical analysis. We solved all reserve selection problems to within `r (gurobi.params.LST[[MODE]]$MIPGap*100)` % of optimality using the $\texttt{rapr}$ R package [@r465] and $\texttt{Gurobi}$ [@r463].

To address the first aim--to determine if the environmental and geographic variables are effective surrogates for adaptive and neutral genetic variation--we generated a collection of single-species prioritizations. For each species, we first generated two sets of prioritizations using increasing environmental and geographic-based targets (separately). Prioritizations were generated using the following surrogate-based targets: `r paste(rapr.params.LST[[MODE]]$surrogate.target,collapse=', ')`. We then create a set of null expectations with which to compare the surrogate-based prioritizations. These null expectations represented possible solutions obtained using conventional conservation planning methods that just use amount (eg. Marxan). For each species, for each target, we generated `r ` prioritizations by randomly selecting planning units occupied by the species. The number of randomly selected planning units was set to equal the number of planning units in the optimal prioritizations.

To address the second aim--to determine if the use of surrogate-based targets can actually improve prioritizations in real-world conservation planning scenarios--we investigated the effectiveness of surrogate-based targets using three scenarios with increasing levels of complexity. To assess the benefits of surrogate-based targets under the simplest of circumstances, our first scenario involved generating single-species prioritizations for each species. However, most large-scale prioritizations involve a comprehensive set of species. By forcing solutions to secure individuals in multiple communities, this may result in prioritizations that secure a greater proportion of intra-specific genetic variation for each species. To test for this effect, our second scenario involved generating multi-species prioritizations. Finally, most large-scale prioritizations also explicitly consider opportunity cost to ensure that prioritizations are cost-effective. Our third scenario involved generating multi-species prioritizations that satisfied targets for minimal opportunity cost.

For each scenario, we generated three types of prioritizations using (1) only amount-based targets, (2) both amount- and surrogate-based targets, and (3) both amount- and genetic-based targets. The purely amount-based prioritizations served as our baseline--representing the prioritizations typically generated in conservation planning exercises. We used `r (rapr.params.LST[[MODE]]$scenario.analysis$amount.target*100)` % amount-based targets in all prioritizations to ensure an adequate proportion of habitat was secured for each species. Based on the previous analysis, we set surrogate-based targets as `r (rapr.params.LST[[MODE]]$scenario.analysis$surrogate.target*100)` % and genetic-based targets as `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` % to ensure that most of the variation was secured for each species. To accomodate variation in the high number of optimal solutions for the single-species amount-based prioritizations, we generated `r (rapr.params.LST[[MODE]]$scenario.analysis$single.species.amount.replicates)` replicate prioritizations.

We then counted the number of species that were sufficiently represented in terms of their adaptive and neutral genetic variation (genetic variation secured $\geq$ `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` %) for each prioritization. We used a global $G$ test to assess whether the proportion of species that met their genetic target in a given prioritization depended on the combination of targets used to generate the planning units (amount-based targets, amount and surrogate-based targets, amount and genetic-based targets), the planning scenario (single-species, multi-species, multi-species with cost), or the type of genetic variation measured (adaptive or neutral). We also conducted a post-hoc analysis involving pairwise $G$ tests (using the \texttt{RVAideMemoire R} package; r@483).

>>>>

Here we investigate the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation in the context of conservation planning. First, we aim to verify if environmental and geographic variables correlate with broad-scale patterns in adaptive and neutral variation (respectively). Although these variables may correlate with genetic variation, they may not be effective surrogates if the level of correlation is not high enough or due to spatial auto-correlative effects. Second, we aim to verify that environmental and geographic variables are effective surrogates for adaptive and neutral variation (respectively). We expect that prioritizations generated using surrogate-based targets will secure more genetic variation than prioritizations generated using only amount-based targets with the same number of planning units. Third, we aim to determine if the addition of surrogate-based targets to conservation planning exercises can result in more effective prioritizations. We expect that prioritizations generated using amount- and surrogate-based targets will sufficiently preserve the genetic variation of more species than those generated using only amount-based targets. If these surrogates can improve the intra-specific genetic variation captured in a prioritization, then conservation planners may use these surrogates when genetic data is not available, and in turn deliver more effective protected areas.

## Methods
### Study system
We used species distribution and genomic data collected by the IntraBioDiv project in the European Alps [@r451; see @r452 and @r478 for further explanation of data collection methods]. This data set contains genetic data for a diverse range of species that were collected using a standardized sampling regime. Additionally, the data set covers a large geographic domain that spans across a range of attitudinal gradients. As a consequence, there is large environmental variation among the grid cell cells which is desirable to assess effectiveness of environmental variables as surrogates for adaptive genetic variation. Thus this data set was particularly well suited for our study.

The IntroBioDiv project data set contains data for 27 alpine plant species that was collected using a 20' longitude by 21' latitude grid (approx. 22.3 km $\times$ 25 km; Figure S1). Project members visited every second grid cell, and if a species was detected in a cell, samples were collected from three individuals. They genotyped samples using amplified fragment length polymorphisms [AFLP; @r453], and constructed matrices denoting the presence/absence of polymorphisms at loci for each species (mean `r mean(sapply(spp.StructureData.LST, n.loci))` \pm `r sd(sapply(spp.StructureData.LST, n.loci))` SD markers genotyped per species; see Table 1 in r@478 for the number markers for each species). Although AFLPs are not ideal as genomic representatives (cf. single nucleotide polymorphisms; SNPs), no multi-species genomic data set with similar properties currently exists. Thus the data set contains information describing the genomic properties of individuals for each species present in every second grid cell.

This data set has previously been used to address a range of different questions. Many studies have used this data set to explore patterns of adaptive [@r484; @r475; @r455; @r451; r@485] and neutral genetic variation [@r451; @r478; @r486]. However, to our knowledge, only a single study has used this data set to explore the effectiveness of a surrogate in the context of conservation planning. Taberlet et al. [-@r486] investigated whether prioritizations generated using the spatial distribution of a comprehensive set species (> 300) could adequately secure the intra-specific genetic variation for 27 species. They found that the prioritization based on species distributions was substantially different to that based on genomic data. Their results suggest that prioritizations based on species distribution data alone will be unable to secure intra-specific genetic variation.

### Landscape data
We examined the effectiveness of environmental and geographic surrogates for adaptive and neutral genetic variation (respectively). We used the grid cells used to sample genetic data as planning units to develop prioritizations. We used only planning units that contained at least a single individual ($n = `r nrow(grid.DF)`$) to reduce computational burden. To examine the potential effects of cost, we calculated the total human population density inside each planning unit [obtained at 1 km resolution from the Global Rural-Urban Mapping Project; \texttt{GRUMP V1}; @r472] and used this to represent acquisition cost.

To describe the geographic location of each grid cell, we projected the grid into an equi-distant coordinate system ($\texttt{ESRI:102031}$), calculated their centroids, and extracted their two-dimensional coordinates. Thus we constructed two-dimensional geographic space-wherein each planning unit occupies a single point--as a potential surrogate for neutral genetic variation.

To describe the environmental characteristics of each grid cell, we obtained data for 19 bioclimatic variables across the study area [approx. 1 km resolution; @r33]. We used this data set in particular because it is commonly used in conservation planning to characterize environmental variation in conservation planning. These layers and the planning units were projected into an equal-area coordinate system ($\texttt{ESRI:102014}$). The 19 bioclimatic variables were clipped to the grid and subject to a principal components analysis (PCA; using \texttt{ArcMap} version 10.2.2; Table S1) to extract the main themes of environmental variation among the grid cells. The first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components (PCs) cumulatively explained `r round(pca.DF[[4]][surrogate.params.LST[[MODE]]$number.components],1)` % of the variation and were used to generate `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` new layers. We calculated the average value for each PC layer in each planning unit, and used these values to characterize climatic variation among the planning units (Figure S2). Thus we constructed a three-dimensional environmental space--wherein each planning unit occupies a single point--as a potential surrogate for adaptive variation.

### Adaptive and neutral genetic data
To investigate the effectiveness of the surrogates for adaptive and neutral genetic variation, we first needed to identify which of the sampled loci--if any--were under selection. We used two outlier detection methods to achieve this. The basic premise underpinning outlier detection methods is that neutral loci are expected to exhibit a specific level of variation among populations, and loci that deviate from this expectation should be under selection [reviewed in @r480]. The advantage of these methods--in contrast with environmental association analyses [eg. @r475]--is that they do not use environmental data to identify loci under selection, which would have biased our analysis. We omitted the species \textit{`r missing.species`} from all subsequent analysis because it was only associated with one genetic lineage and thus not compatible with one of the outlier detection methods. Loci identified as outliers in both analyses were treated as adaptive, and the remaining loci were treated as neutral.

First, we used multinominal-Dirichlet models implemented in \texttt{BayeScan} [version 2.1; @r456] to identify loci under selection. We adopted a similar methodology to Bothwell _et al._ [-@r455] and applied it to each of the species in the data set. To avoid falsely classifying loci as adaptive, we grouped individuals into genetic lineages for each species (Figures SXXX--SXXX). We used the number of genetic lineages in each species previously identified by Alvarez _et al._ [-@r478]. For each species, we used \texttt{Structure} (version 2.3.1; using same parameters as @r478 per run with `r structure.params.LST[[MODE]]$numruns` runs per species) and \texttt{ClumPP} (version 1.1.2; @r459) to group individuals into populations. We then ran $\texttt{Bayescan}$ for each species using these groupings [1:1 prior odds; `r bayescan.params.LST[[MODE]]$nbp` pilot runs; `r bayescan.params.LST[[MODE]]$burn` burn-in iterations; `r bayescan.params.LST[[MODE]]$n` post-burn-in iterations thinned by `r bayescan.params.LST[[MODE]]$thin` iterations; @r456]. To avoid false-positives, we omitted loci where the global frequency of the minor allele was $\geq 0.05$ (following guidelines in the user manual) and assumed they were neutral. Additionally, we omitted individuals from this analysis when their population membership was uncertain (maximum membership probability $< `r structure.params.LST[[MODE]]$probability.threshold`$). We ran `r bayescan.params.LST[[MODE]]$reps` replicates per species using a suitable false discovery rate [FDR $\leq `r bayescan.params.LST[[MODE]]$fdr`$; @r466].

Second, we used PCAs to identify outlier loci using methods implemented in the \texttt{pcadapt R} package [version 2.2; @r487]. For each of the 26 species, we ran a PCA and extracted the minimum number of components needed to secure `r pcadapt.params.LST[[MODE]]$min.variance.explained` % of the variation in loci. We then computed Mahalanobis distances [@r398] to detect outlier loci ($P < `r pcadapt.params.LST[[MODE]]$alpha.level`$). To enable comparisons between the two outlier detection analyses, we used the same individuals in this analysis as used in the $BayeScan$ analysis.

After classifying loci as adaptive or neutral, we mapped the main gradients of the adaptive (if detected) and neutral genetic variation for each species (Figures S6--S32). For each species, we discarded the population groupings, and partitioned adaptive and neutral loci into separate data sets. We used non-metric multi-dimensional scaling [NMDS; implemented in the \texttt{vegan R} pacakge; @r458] using Gower distances [@r464; using the \texttt{cluster R} package to accommodate sparsity; @r457] to derive continuous variables that described the main gradients of adaptive and neutral genetic variation for each species (Table S2). To ensure that the ordinations described a sufficient amount of the genomic variation, we ran successive scaling analyses with increasing dimensionality until this was achieved (maximum stress value $\leq$ `r nmds.params.LST[[MODE]]$max.stress`; `r nmds.params.LST[[MODE]]$trymax` random starts for each analysis). Since each grid cell had up to three samples per species, we used the average of the ordinated values associated with the individuals in each grid cell to express the typical genomic characteristics of individuals in the cells.

The previous analyses resulted in an adaptive (if detected) and neutral genetic space for each species. For a given species, each planning unit occupied by the species was associated with a multi-dimensional point in the species' neutral genetic space. Planning units that were closer together in this space are occupied by individuals with similar neutral genetic loci. Similarly, if the species was associated with adaptive loci, each planning unit occupied by the species was associated with a multi-dimensional point in the species' adaptive genetic space. By spreading out conservation effort across a given genetic space for a given species, prioritizations can secure more genetic variation [see @r465 for discussion on attribute spaces].

### Prioritizations and statistical analyses
We used the unreliable representative and adequate prioritization (URAP) formulation of the reserve selection problem [@r465]. This formulation can identify the minimum number of planning units required to preserve both a proportion of the species' range (using amount-based targets) and a proportion of variation found across the species' range [using space-based targets and attribute spaces; _sensu_ @r465]. We treated the environmental and geographic surrogate variables as separate attribute spaces. We also treated the adaptive (if detected) and neutral variables as separate attribute spaces for each species. We set the demand points for each species and each attribute space using the values associated with the planning units. For every prioritization we generated, we calculated the proportion of the adaptive (if detected) and neutral genetic variation that every prioritization secured to assess its performance. Prioritizations associated with negative values--because they secured only a very small amount of genetic variation--were replaced with zeros to facilitate statistical analysis. We solved all reserve selection problems to within `r (gurobi.params.LST[[MODE]]$MIPGap*100)` % of optimality using the $\texttt{rapr}$ R package [@r465] and $\texttt{Gurobi}$ [@r463].

To address the first aim--to determine if the environmental and geographic variables correlate with adaptive and neutral genetic variation--we fit maximum likelihood population-effects (MLPE) models [implemented in the \texttt{ResistanceGA R} package; @r488]. We computed differences between the grid cells in terms of their environmental conditions and  geographic position. Additionally, for each species, we computed the differences between the grid cells in terms of the adaptive and neutral genetic characteristics of individuals that inhabited them (if detected). All differences were calculated using Euclidean distances. We then fit a set of MLPE models to the differences in the adaptive genetic characteristics among the grid cells and the differences in the environmental conditions for each species associated with adaptive genetic variation. We also fit a set of similar models using the differences in neutral genetic characteristics and the geographic distances for each species. For each model we fit an intercept-only null model, and tested surrogate variables whether they explained substantially more variation using $\chi^2$. We then applied Bonferroni corrections to each set of models (separately). Note that this analysis does not take into account spatial auto-correlation. The subsequent analyses explicitly control for this effect.

To address the second aim--to determine if the environmental and geographic variables are effect surrogates for adaptive and neutral genetic variation--we generated a collection of single-species prioritizations. For each species, we first generated two sets of prioritizations using increasing environmental and geographic-based targets (separately). Prioritizations were generated using the following surrogate-based targets: `r paste(rapr.params.LST[[MODE]]$surrogate.target,collapse=', ')`. We then create a set of null expectations with which to compare the surrogate-based prioritizations. These null expectations represented possible solutions obtained using conventional conservation planning methods that just use amount (eg. Marxan). For each species, for each target, we generated `r ` prioritizations by randomly selecting planning units occupied by the species. The number of randomly selected planning units was set to equal the number of planning units in the optimal prioritizations.

To address the third aim--to determine if the use of surrogate-based targets can actually improve prioritizations in real-world conservation planning scenarios--we investigated the effectiveness of surrogate-based targets using three scenarios with increasing levels of complexity. To assess the benefits of surrogate-based targets under the simplest of circumstances, our first scenario involved generating single-species prioritizations for each species. However, most large-scale prioritizations involve a comprehensive set of species. By forcing solutions to secure individuals in multiple communities, this may result in prioritizations that secure a greater proportion of intra-specific genetic variation for each species. To test for this effect, our second scenario involved generating multi-species prioritizations. Finally, most large-scale prioritizations also explicitly consider opportunity cost to ensure that prioritizations are cost-effective. Our third scenario involved generating multi-species prioritizations that satisfied targets for minimal opportunity cost.

For each scenario, we generated three types of prioritizations using (1) only amount-based targets, (2) both amount- and surrogate-based targets, and (3) both amount- and genetic-based targets. The purely amount-based prioritizations served as our baseline--representing the prioritizations typically generated in conservation planning exercises. We used `r (rapr.params.LST[[MODE]]$scenario.analysis$amount.target*100)` % amount-based targets in all prioritizations to ensure an adequate proportion of habitat was secured for each species. Based on the previous analysis, we set surrogate-based targets as `r (rapr.params.LST[[MODE]]$scenario.analysis$surrogate.target*100)` % and genetic-based targets as `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` % to ensure that most of the variation was secured for each species. To accommodate variation in the high number of optimal solutions for the single-species amount-based prioritizations, we generated `r (rapr.params.LST[[MODE]]$scenario.analysis$single.species.amount.replicates)` replicate prioritizations.

We then counted the number of species that were sufficiently represented in terms of their adaptive and neutral genetic variation (genetic variation secured $\geq$ `r (rapr.params.LST[[MODE]]$scenario.analysis$genetic.target*100)` %) for each prioritization. We used a global $G$ test to assess whether the proportion of species that met their genetic target in a given prioritization depended on the combination of targets used to generate the planning units (amount-based targets, amount and surrogate-based targets, amount and genetic-based targets), the planning scenario (single-species, multi-species, multi-species with cost), or the type of genetic variation measured (adaptive or neutral). We also conducted a post-hoc analysis involving pairwise $G$ tests [using the \texttt{RVAideMemoire R} package; r@483].
